### 2016-11-08 src/4_OnlineLearning.tex
inicio revision profe
revision page 2

ML models are often more accurate than what can be created through direct programming. The reason is that ML models are data driven and are able to examine large amounts of data.

@@

In this thesis we will emphasise the supervised learning problem since it is the most common way of modelling financial problems.

@@

$$
S= \{(x_1,y_1),\,(x_2,y_2),\dots\,,\,(x_n,y_n)\} \in \mathcal{S}, (x_i,y_i) \in X\times Y \quad \forall i = 1..n
$$

\noindent where $\mathcal{S}$ is the space of instances, $X \subseteq \mathbb{R}^m$ and $Y = \mathbb{R}$ in case of regression problems and $Y = \{1,-1\}$  if it is a classification problem.

A learning algorithm $\mathcal{A}$ takes as input a data set $S \in \mathcal{S}$ and output a function $f_S$:

\begin{eqnarray*}
\mathcal{A}: \mathcal{S} &\rightarrow & \mathcal{H} \\
S &\rightarrow &\mathcal{A}(S) = f_S
\end{eqnarray*}

\noindent where $\mathcal{H}$ is called the {\em hypothesis space}, is the space of functions that the algorithm is allowed to search. The selection of $f_S$ is based on a loss function $V(f(x),y)$ the expected risk, which has to be minimised.

>>>>

ML models are often more accurate than what can be created through direct programming. The reason for this is that ML models are data driven and are able to examine large amounts of data.

@@

Supervised learning is most popular and most commonly used in modelling financial problems and the assessments of this method and their results in practice are fairly good. Therefore, in this thesis we will adhere to this trend and we will use supervised learning.

@@

$$
S = \{ (x_k,y_k)\in X\times Y : k=1,...,n \}
$$

\noindent where $X \subseteq \mathbb{R}^m$ and $Y = \mathbb{R}$ in case of regression problems and $Y = \{1,-1\}$  if it is a classification problem.

A learning algorithm $\mathcal{A}$ takes as input a data set $S \in \mathcal{S}$ and outputs a function $f$:

\begin{eqnarray*}
\mathcal{A}: \mathcal{S} &\rightarrow & \mathcal{H} \\
S &\rightarrow &\mathcal{A}(S) = f
\end{eqnarray*}

\noindent where $\mathcal{H}$ is called the {\em hypothesis space}, is the space of functions that the algorithm is allowed to search. The selection of $f_S$ is based on the minimization if the expected risk of the loss function $V(f(x),y): \R\times\R\to\R$.
